Paper 1 Analysis

### 2016-04-24 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Evaluated UK (kl)e model for boundary issues.

@@

>>>>

%++++++++++++++++++++++++++++++
\subsection{Portugal} 
\label{sec:boundary_portugal}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{United Kingdom} 
\label{sec:boundary_uk}
%++++++++++++++++++++++++++++++

Many other modeling approaches estimate parameters that are close to, 
but not exactly on, a boundary. 
One example is the modeling approach for the UK wherein
all factors of production are quality-adjusted,
the $(kl)e$ nesting structure is employed, and the CSP is rejected.
The best fitting value of $\delta_1$ rounds to 
\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$delta_1, 3), nsmall = 3)},
and the best fitting value of $\delta$ rounds to
\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$delta, 3), nsmall = 3)}.
So, it does not appear that the UK model is near a $\delta_1$ or $\delta$ 
boundary in this instance.
Nor is it near a $\rho_1$ or $\rho$ boundary. 
Again, to three decimal places,
$\rho_1$ is 
\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$rho_1, 3), nsmall = 3)},
and 
$\rho$ is
\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$rho, 3), nsmall = 3)}.
This model is clear of any boundaries.
